\documentstyle[12pt,fullpage]{article}
%
\newcommand{\texx}{{\tt texx}}
\newcommand{\texsun}{{\tt texsun}}
\newcommand{\dvi}{{\tt dvi}}
\newcommand{\iptex}{{\tt iptex}}
%
\title{DVI Output Guide}
\author{
Dirk Grunwald \\
Dept. of Computer Science\\
University of Illinois
}
\date{Sept. 1987}
%
\begin{document}
\maketitle
\begin{abstract}
This document describes the features, use and installation of
\iptex, \texx\  and \texsun.
\iptex\ prints \dvi\ \TeX\ documents on an Imagen printer.
\texx\ is a document previewer which uses the X-11 window system.
\texsun\ is a document previewer under the SunView window system.
\iptex\ was written by Chris Torek at the University of Maryland.

Additionally, this version of \texx\ would not exist without the work of
Steve Eichin at MIT and Chris Torek at the U. of Maryland.

\texsun\ is the original work of the author.

{\bf: NOTE - this documentation is somewhat out of date, and carries no
information about TeXx2}
\end{abstract}
%
\section{Introduction}
This document is structured into two major sections.
The first of these is a users manuals for \iptex, \texx and \texsun,
and is the only section of interest for most people.
The second section covers the installation and customization of
the package.

\section{Users Guide}
In the manuals which follow, it is assumed that you have followed your
local guide to produce a \dvi\ file from your \TeX\ or \LaTeX\ document.
The first manual describes \iptex, used to print your \dvi\ file
on an Imagen printer.
The second manual describe \texx\ and \texsun.
\input{iptex.tex}
\input{texx.tex}

\newpage
\section{Installation Guide}
This section of the guide should be ignored by users.
It pertains to installing \iptex\ and \texx\,\texsun, and porting
the code to new hardware.
\input{installation.tex}
\end{document}
