%
%	Copyright (c) Japan TeX Users Group, 1986 1987
%
\magnification=\magstephalf
\newdimen\hpos
\def\setpos#1#2{\leftskip=#1\parindent\hpos=#2\parindent}
\def\xitem#1{\hangindent\hpos\noindent\rlap{#1}\hskip\hpos}
\def\title#1{\medskip\leftskip=0pt\leftline{\bf#1}}
\def\option#1{\medskip\setpos{1}{5}\xitem{\tt#1}}
\rightskip=\parindent

\title{NAME}
texpr --- print out dvi-file to LBP-8

\title{SYNOPSIS}
{\tt texpr} [{\it options\/}] {\it dvi-file}

\title{DESCRIPTION}
\setpos{1}{1}\noindent
Texpr is a program which converts the dvi file to a sequence 
of LBP-8 commands and sends them to the printer.
Texpr spools dvi file like lpr.
Logical device name to which texpr outputs is {\it lp} (site dependent).
Extension {\tt.dvi} can be omitted in the file specification.

\option{-p  $n_1[,n_2[,n_3]]$}
Print from $n_1$ page to $n_2$ page. And $n_3$ is a even-odd specifier.
You can specify 2 or 1 or 0 for $n_3$. Each value means even page,
odd page, both page respectively. (Default is 0.)
Some examples are shown below.

\smallskip\setpos{6}{3}
\xitem{\tt-p 5     } from 5 page to end page\par
\xitem{\tt-p 5,10  } 5,$\cdots$,10 page\par
\xitem{\tt-p 5,11,1} 5,7,9,11 page\par
\xitem{\tt-p 1,1   } 1 page only\par
\xitem{\tt-p 5,,2  } 6,8,10,12,$\cdots$,end page\par

\option{-r}
Print in reverse order of page. (As you know, LBP-8 stacks paper
in face up manner.)

\option{-t  $[\pm]n$}
Move top margin position $n/100$ inch down from default position.
Move up if negative. For example,

\smallskip\setpos{6}{3}
\xitem{\tt-t 50} move top margin position 1/2 inch down\par

\option{-l  $[\pm]n$}
Move left margin position $n/100$ inch right from default position.
Move left if negative. For example,

\smallskip\setpos{6}{3}
\xitem{\tt-l -25} move left margin position 1/4 inch left\par

\smallskip\setpos{1}{5}
\xitem{}
(When you use manual paper feed, you had better specify {\tt-t 20 -l -10}
to correct registration position.)

\option{-d}
Force down load. Usually texpr searchs for the most frequently used font,
and then checks whether the same font name is written in .down\_font
file. Texpr does font loading only if not same. But this option force
down loading even if same. (You should use this option after printer power
on.)

\option{-m$x$}
Use this magnification value instead of one in the dvi file.
Following 7 formats are available.

\smallskip\setpos{6}{3}
\xitem{\tt-m0} $\times 1$ magnification\par
\xitem{\tt-mh} $\times \sqrt{1.2}$ magnification\par
\xitem{\tt-m1} $\times 1.2$ magnification\par
\xitem{\tt-m2} $\times 1.2^2$ magnification\par
\xitem{\tt\ \vdots}\par
\xitem{\tt-m5} $\times 1.2^5$ magnification\par

\option{-c  $n$}
Specify number of copies.

\option{-v}
Verbose mode. Various messages are output to your terminal.

\option{-h}
Use paper with long side horizontal.
(CAUTION! This option is for only AJ2 model, and rather slow.)

\title{FILES}
\setpos{1}{10}
\xitem{\tt/usr/local/lib/dvi2lbp} d-filter\par
\xitem{\tt/usr/lib/tex/fonts/*.*pxl} font file\par
\xitem{\tt/usr/lib/tex/fonts/*.*pk} new format font file\par
\xitem{\tt/usr/lib/tex/fonts/.down\_font} memo file\par

\title{SEE ALSO}
tex(1)
\title{BUGS}
no accounting

\bye

